Beam test performance of the highly granular SiW-ECAL technological prototype for the ILC.

### 2019-04-30 performance-paper-draft/NIMsub_arxiv1902.00110/v1/draft.tex
v1, with shower study

%\documentclass[a4paper,11pt]{article}
\documentclass[final,3p,times,twocolumn]{elsarticle}
%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

@@

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{lineno}
\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{{#1}}}
\usepackage[outdir=./]{epstopdf}
\usepackage{upgreek}
\usepackage{amsmath}
%\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}

@@

\begin{abstract}
The technological  prototype of the CALICE highly granular silicon-tungsten electromagnetic 
calorimeter (SiW-ECAL) tested in beam at DESY in 2017. 
In this test the setup comprised seven layers of 1024 channels and a size of $18\times18$ cm$^2$ each.
This article presents key performance results in terms of signal over noise ratios at different levels of the readout chain 
and a study of the uniformity of the detector response.   
\end{abstract}

@@

The International Linear Collider, ILC \cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya},
is a next generation of $e^{+}e^{-}$
linear colliders project. It will
provide collisions of polarized beams with center-of-mass energies between 250 GeV and 1 TeV.
These collisions will be studied by multipurpose detectors.
The two proposed projects~\cite{Behnke:2013lya} --  the International
Large Detector (ILD) and the Silicon Detector
(SiD) -- are designed for the use of Particle Flow (PF) technique  \cite{Brient:2002gh,Morgunov:2004ed}, for the
reconstruction of the final state particles.
The PF techniques rely on single particle separation
to allow for the selection of the best information available
in the full detector to determine the final states of the collisions.
They allow reducing the impact of the poor resolution of the calorimeter systems
(compared with trackers) in the overall reconstruction
but require detectors with highly granular, compact
and hermetic calorimetric systems. Furthermore, the PF capabilities are enhanced when the calorimeters
are placed inside a large magnetic field that favors the separation of charged particles. 
This in turn calls for a compact design of the calorimeters.
Most of the R\&D efforts of such calorimeters 
for future linear colliders are carried out by the CALICE collaboration.

@@

\begin{figure*}[!ht]
\centering
\begin{tabular}{l}
  \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
  \includegraphics[width=0.75\textwidth]{mapping-eps-converted-to.pdf} \\
\end{tabular}
\caption{Top: prototype with 7 layers inside the mechanical housing. Bottom: schematic view of the readout modules
  including the surface repartition readout by each ASIC, numbered from 0 to 15. Notice that the adapter board and DAQ-detector interface drawings are not at scale.}
\label{proto}
\end{figure*}

A picture showing the SiW-ECAL technological prototype setup tested at DESY (Hamburg) in summer
2017 can be seen in Figure \ref{proto}.
The setup consists of 7 layers housed in a PVC and aluminum structure that can host up to 10 layers
in slots with a $15-$mm pitch. The first six layers were placed in the first six slots
and the 7th in the last one.
From now on, the layers will be referenced by their numbers from 1 to 7.
The detector was commissioned in the laboratory
and afterwards exposed to a low energy positron beam in the DESY test beam area (line 24) \cite{Diener:2018qap} the first layer located at the most upstream on the beam.
All results presented here are obtained with the detector running in power pulsing mode
and with gated acquisitions of $1-3$ ms at frequencies of 1-5 Hz.

Each layer consists of a readout module
on top of a carbon cradle that protects the sensors
and the sides of the module. The readout module is further wrapped by two aluminum plates
that provide electromagnetic shielding and mechanical stability.
The readout module itself consists of an Active Signal Unit (ASU) and an adapter board
to a data acquisition system (DAQ)\cite{Gastaldi:2014vaa,Rubio-Roy:2017ere,Magniette:2018wdz} at the beginning of the module.
In the picture, the ASU is covered 
by an aluminum plate marked by the red number 1.
The ASU consist of a $18\times18$ cm$^2$ sized printed circuit board, PCB,
equipped with 16 VFE ASICs and 4 silicon sensors glued onto the other side.
The PCB features 1024 square pads of $5.5\times5.5$ mm$^2$ that are readout by the ASICs.
Part of the adapter board is also covered by the aluminum plate and the uncovered part 
is seen over the red number 2 in the picture. 
The adapter board also holds other
services e.g. the super capacitance used for the power pulsing. 
This decoupling capacitor of 400 mF with 16 m$\Omega$ of equivalent serial resistance
provides enough local storage 
of power to assure stable low voltage supply during the power pulsing. This capacitor
is seen just above the red number 2.
The first component
of the DAQ system, the detector interface board described in \cite{Gastaldi:2014vaa}, is identified in the picture by a red
number 3.
For simplicity, the rest of the DAQ system is not shown.

The VFE ASICs are 16 SKIROC2 \cite{Callier:2011zz,Amjad:2014tha,Suehara:2018mqk}
(Silicon pin Kalorimeter Integrated ReadOut Chip), 
that have been designed for the readout of silicon PIN diodes.
The SKIROC2 in LFBGA package are bump bonded to the PCB.
The version of the ASUs tested in this beam test has a thickness
of 2.8 mm including the ASICs in its current packaging.
Each of these SKIROC2 comprises 64 readout channels
made of a variable-gain preamplifier followed by two branches:
a fast line for the self-trigger decision and a slow line for dual-gain charge measurement.
The gain on the preamplifier is set by changing the feedback capacitor, $C_{f}$.
The fast line consists of a high gain variable CRRC shaper followed by
a low offset discriminator to make the trigger decision.
A common 10-bit DAC provides the threshold of the discriminator.
The slow line is made of a low gain and a high gain CRRC
shapers to handle a large dynamic range.
When a channel triggers, a track and hold cell is used to record the signal at its peaking time
in the dual gain line. The levels of all the others
channels are then also recorded.
% A bandgap ensures the stability with
%respect to supply voltage and temperature for all the requested
%references in the analogue core.
The triggers are timestamped within each gated acquisition with a slow clock
of 5 MHz. The timestamp numbers are called brunch crossing identifiers (BCID).
The charges are stored in the buffers of a switched capacitor array, SCA, and later converted by a 12-bit Wilkinson ADC.
The ASIC consumes, in the power pulsing conditions as foreseen for the ILC, 
27 $\upmu$W per channel.

The four sensors consist of $90\times90$ mm$^{2}$ silicon sensors of
320$\pm15\,\upmu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
Each sensor is subdivided in an array of 256 PIN diodes of $5.5\times5.5$ mm$^2$
connected each to the PCB pads by a dot of conductive glue.
The high voltage to deplete the sensors is delivered to the sensors via a
100 $\upmu$m copper foil isolated from the rest of the setup by a kapton sheet.
It has been estimated that
a MIP traversing the PIN perpendicular to its surface produces, in average,
a signal of 4 fC.

@@

\begin{enumerate}
\item Calibration without tungsten absorber using 3 GeV positrons interacting, in the first approach, as MIPs.
  The beam was normally directed to 81 positions equally distributed over the modules surface.
\item Test in a magnetic field up to 1 T using, also without tungsten and with 3 GeV positrons. For this test, a PVC structure was
designed and produced to support one single readout module.	
%The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
%readout module itself are able
%to handle strong magnetic fields; 
%second to check the quality of the data and the performance of the detector during the data taking when running
%in a magnetic field.
\item Response to electrons of different energies with a fully equipped detector, {\it i.e}\@. sensitive parts {\it and} tungsten absorber. 
\end{enumerate}

In this paper, we discuss in detail the results of the commissioning of the prototype in Section \ref{sec:commissioning}
and the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
We also show the results on the pedestal and noise stability when the readout modules are placed inside
a magnetic field, in Section \ref{sec:magnetic}. %The study of the performance of the detector
%for electromagnetic shower events is not covered in this document and will be the topic of a future paper.

@@

\begin{figure}[h!]
  \includegraphics[width=0.5\textwidth]{masked_layer-eps-converted-to.pdf} 
\caption{Fraction of channels with counts above one MIP in noise runs and that have been disabled for the data taking.}
\label{noisycells}
\end{figure}

@@

The threshold of the internal trigger can be optimized by means of dedicated scans of trigger threshold values
with only noise signals or with injected signals of different amplitudes.
%In the absence of external signals,
%the shape and position of the threshold scan curves shows the
%full envelope of the noise in the fast shaper which
%not only depends on the electronic noise but also on the slow clock frequency, making its interpretation
%not clear. 
The trigger thresholds used for data taking of the individual channels
are determined by lowering successively the trigger thresholds of the
channels and recording the number of counts. The resulting curves can be approximated by an inverted error function.
%Anyway, as the first goal is to set the trigger thresholds high enough to filter out most of the
%noise events independently of its origin, we made the optimization of the trigger threshold values by performing dedicated
%threshold scan runs with only noise. For that end, for a fixed amount of time, we counted the times that
%every channel recorded at least one trigger as a function of
%the internal trigger threshold. The resulting curve of acquisitions with triggers vs trigger threshold was
%interpreted as the integral of the noise spectrum, assumed as gaussian.
A value of the optimal threshold was calculated for every channel by shifting the threshold
from the threshold at the 50\% of the curve plus 3 times the width of the curve, 
with the width defined as half the difference between the thresholds
at which the curve is equal to $50\pm34\%$. The average of the optimal thresholds for all channels
is used as the optimal global threshold to be used by the ASIC.
If the analysis has failed in more than 50\% of the channels ({\it i.e.} because they are masked),
an {\it ad-hoc} high value of the threshold is chosen for the ASIC (250 in DAC units).

Note here that the width of the curve defined before depends on the ratio
of the frequency of the white noise of the electronics and the clock speed of the readout.
Therefore, the width is not a proper measurement of the detector noise.
To achieve this the scan has to be repeated with external signals.
These can either be provided by signals generated by beam particles or by injecting signals into the channels.
Here we follow the second approach. Amplitudes equivalent to 1 and 2 MIPs were injected into channels of an ASIC mounted on a testboard.

%With this procedure, we fulfill the first requirement: set the trigger thresholds high enough to filter the noise.
%We still need to know what is the size of signals that we can trigger on.
%For this we need to perform a calibration of the trigger thresholds
%and for that we need to perform the scans with calibrated external signals as input.
%We planned to do this with beam particle by performing
%scans with the beam hitting the detector at different angles. Unfortunately, due to tightness
%of the program this could not be done
%at the beam test described in this document. Instead
%we used injected signals directly on the SKIROCs. Again we face the issue that
%this capability is not included in all our modules so
%we did it in a SKIROC testboard \cite{Suehara:2018mqk} in which a single SKIROC2 in BGA package is placed and signals of
%the equivalent size of the expected for 1 MIP and 2 MIPs
%are directly injected in the preamplifier (via a 3 pF capacitor located in the injection line).
The result of these scans is shown in Figure \ref{scurves_injection} for several channels of one SKIROCs.
These curves allow for the trigger threshold calibration and the
estimation of signal-over-noise ratio for the trigger, $(S/N)_{trigger}$, defined as the ratio between the distance of the
1 MIP and 2 MIP threshold curves scans at its 50\% of efficiency and the width of the 1 MIP threshold scan curve.
From the measurement shown in Figure \ref{scurves_injection} we extract a $(S/N)_{trigger}$ ratio of about 12.8.

\begin{figure}[h!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=0.35\textwidth]{scurve_pp_fastshaper_ch_DAC-eps-converted-to.pdf} \\
	\end{tabular}
\caption{Threshold curves with charge injection (1 MIP in blue and 2 MIPs in red) for different channels in a SKIROC2 testboard. From this plot, we extract a $(S/N)_{trigger}$ of about 12.8 in the trigger line.}
\label{scurves_injection}
\end{figure}

@@

\begin{figure}[h!t]
  \centering
  \includegraphics[width=0.5\textwidth]{threshold_chip-eps-converted-to.pdf}
  \caption{Summary of the trigger threshold settings in the internal DAC units and in MIP units.}
\label{trigger_thresholds}
\end{figure}

@@

All the analyses presented here rely on the selection and identification
of tracks-like events. The first step of the reconstruction is the rejection
of two types of fake events due to the ASIC
design: {\it a)} triggers in consecutive BCIDs
due to the preamplifiers sensitivity to instabilities of the power supply; {\it b)}
an artifact of the event validation logical sequence of the ASIC. These fake
events are removed offline using timing information.
Residual electromagnetic showers are rejected by requiring
less than 5 triggers per module.
Tracks are therefore reconstructed by creating clustered
events from the seven layers grouped using their time stamp, allowing for a
tolerance on the BCID of $\pm1$. An event is accepted if at least
three of the layers were clustered together in a track traversing the modules in the
same position
for all modules with a tolerance of $\pm5.5$ {\rm mm} per layer.

@@

\begin{figure}[!t]
  \centering 
  \includegraphics[width=0.5\textwidth]{efficiency_nhits4_chips-eps-converted-to.pdf} \\
  \caption{MIP detection efficiency in high purity samples of tracks of MIP-like acting particles for all layers. The average for all readout channels in each ASICs is shown. The error bars correspond to the standard deviation of the efficiency distribution of all channels in th ASIC.}
\label{efficiency}
\end{figure}

\subsection{Pedestal and noise stability in a magnetic field}
\label{sec:magnetic}

Data were recorded without magnetic field as reference for values of the magnetic field of 0.5 T and 1T, respectively. 
%The study of the performance of the modules inside
%inside magnetic fields has been divided in three consecutive steps:
%a run with a magnetic field of 1 T; a second run with 0.5 T; and a final run with the magnet off.
The beam, 3 GeV positrons, was incident on the area of the PCB readout by the ASIC number 12.

The pedestal position and width of all channels
in the readout module inside of the magnetic field are compared with
their values obtained in Section \ref{sec:calib}.
This is shown in Figure \ref{pedestal_magnetic}.
We see that the agreement is perfect within the statistical uncertainties.
Due to the lower rates in this beam area, the
analysis is only done up to few memory cells and at least 500 entries are required in order to calculate the pedestals
for comparison with the default values.

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=0.5\textwidth]{1T_summary_pedestal-eps-converted-to.pdf} \\
    \includegraphics[width=0.5\textwidth]{1T_summary_noise-eps-converted-to.pdf}
  \end{tabular}
  \caption{Average deviation of the pedestal mean position (up) and width (down). The error bars correspond to one standard deviation of the averaged values.}
\label{pedestal_magnetic}
\end{figure}

@@

In this document we present the results
on the commissioning in beam of a small but fully equipped SiW-ECAL technological prototype
made of readout modules featuring the main characteristics foreseen for future high energy $e^{+}e^{-}$ collider detectors.
%It is the first time that results obtained with data taken by the SiW-ECAL continuosly
%operated in power pulsing are published.
%For the first time results
% SETUP dedicated for physics program with electromagnetic showers.
For the first time results are presented for detection units featuring 1024 channels as
designed for e.g. the ILD Detector in a setup optimized for a physics program dedicated to the study
of electromagnetic showers. The seven layers under study were operated in power pulsed mode.
Therefore this article constitutes a first reference for the detector performance in this operation mode.  
The beam test has allowed for studying in detail 
the performance of the detector.
The detector response is homogeneous with
98\% of the non masked channels calibrated
at a spread of the 5\%.
The signal over noise on the trigger has been evaluated to be about 12.8, a value that allows to
for setting trigger below the MIP level with high efficiency 
although new dedicated beam tests are required to know the uncertainty and spread
of this value 
among different modules and ASICS.
The signal over noise on the charge measurement for triggered channels is 20.4, which 
ensures that all channels with a trigger just about noise level can be used in the data analysis.
The MIP detection efficiency in tracks has been evaluated to be compatible with the 100\% in most of the channels.

>>>>

%\documentclass[a4paper,11pt]{article}
\documentclass[final,3p,times,twocolumn]{elsarticle}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

@@

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{lineno}
\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{{#1}}}
\usepackage[outdir=./]{epstopdf}
\usepackage{upgreek}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{hyperref}
\hyphenation{time-stamped}
%\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}

@@

\begin{abstract}
The technological  prototype of the CALICE highly granular silicon-tungsten electromagnetic 
calorimeter (SiW-ECAL) has been tested in beam at DESY in 2017. 
In this test the setup comprised seven layers of 1024 channels and a size of $18\times18$ cm$^2$ each.
This article presents key performance results in terms of signal over noise ratios at different levels of the readout chain 
and a study of the uniformity of the detector response.   
\end{abstract}

@@

The International Linear Collider, ILC \cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya},
is a next generation of $e^{+}e^{-}$
linear colliders project. It will
provide collisions of polarized beams with center-of-mass energies between 250 GeV and 1 TeV.
These collisions will be studied by multipurpose detectors.
The two proposed projects~\cite{Behnke:2013lya} --  the International
Large Detector (ILD) and the Silicon Detector
(SiD) -- are designed for the use of Particle Flow (PF) technique  \cite{Brient:2002gh,Morgunov:2004ed}, for the
reconstruction of the final state particles.
The PF techniques rely on single particle separation
to allow for the selection of the best information available
in the full detector to determine the final states of the collisions.
They allow reducing the impact of the poor resolution of the calorimeter systems
(compared with trackers) in the overall reconstruction
but require detectors with highly granular, compact
and hermetic calorimetric systems. Furthermore, the PF capabilities are enhanced when the calorimeters
are placed inside a large magnetic field that favours the separation of charged particles. 
This in turn calls for a compact design of the calorimeters.
Most of the R\&D efforts of such calorimeters 
for future linear colliders are carried out by the CALICE collaboration.

@@

\begin{figure*}[!ht]
  \centering
  \begin{tabular}{l}
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
    \caption{}
    \label{proto:a}
  \end{subfigure}%
  \end{tabular}
  \begin{tabular}{l}
    \begin{subfigure}{\textwidth}
    \centering
    %  \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
    \includegraphics[width=0.75\textwidth]{mapping-eps-converted-to.pdf} \\
    \caption{}
    \label{proto:b}
    \end{subfigure}%
  \end{tabular}
%\begin{tabular}{l}
%  \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
%  \includegraphics[width=0.75\textwidth]{mapping-eps-converted-to.pdf} \\
%\end{tabular}
\caption{(a) Prototype with 7 layers inside the mechanical housing. (b) Schematic view of the readout modules
  including the surface repartition readout by each ASIC, numbered from 0 to 15. Notice that the adapter board and the DAQ-detector interface drawings are not at scale.}
\label{proto}
\end{figure*}

A picture showing the SiW-ECAL technological prototype setup tested at DESY (Hamburg) in summer
2017 can be seen in Figure \ref{proto:a}.
The setup consists of 7 layers housed in a PVC and aluminium structure that can host up to 10 layers
in slots with a $15-$mm pitch. The first six layers were placed in the first six slots
and the 7th in the last one.
From now on, the layers will be referenced by their numbers from 1 to 7.
The detector was commissioned in the laboratory
and afterwards exposed to a low energy positron beam in the DESY test beam area (line 24) \cite{Diener:2018qap} the first layer located at the most upstream on the beam.
All results presented here are obtained with the detector running in power pulsing mode
and with gated acquisitions of $1-3$ ms at frequencies of 1-5 Hz.

Each layer consists of a readout module
on top of a carbon cradle that protects the sensors
and the sides of the module. The readout module is further wrapped by two aluminium plates
that provide electromagnetic shielding and mechanical stability.
The readout module itself consists of an Active Signal Unit (ASU) and an adapter board
to a data acquisition system (DAQ)\cite{Gastaldi:2014vaa,Rubio-Roy:2017ere,Magniette:2018wdz} at the beginning of the module.
In Figure \ref{proto:a}, the ASUs are covered 
by an aluminium plate as the one marked by the red number 1.
Each ASU consist of a $18\times18$ cm$^2$ sized printed circuit board, PCB,
equipped with 16 VFE ASICs and 4 silicon sensors glued onto the other side.
The PCB features 1024 square pads of $5.5\times5.5$ mm$^2$ that are readout by the ASICs.
Part of the adapter board is also covered by the aluminium plate and the uncovered part 
is seen over the red number 2 in Figure \ref{proto:a}. 
The adapter board also holds other
services e.g. the super capacitance used for the power pulsing. 
This decoupling capacitor of 400 mF with 16 m$\Omega$ of equivalent serial resistance
provides enough local storage 
of power to assure stable low voltage supply during the power pulsing. This capacitor
is seen just above the red number 2 in Figure \ref{proto:a}.
The first component
of the DAQ system, the detector interface board described in \cite{Gastaldi:2014vaa},
is identified in Figure \ref{proto:a} by a red number 3.
For simplicity, the rest of the DAQ system is not shown.  A schematic drawing of a readout module
is shown in Figure \ref{proto:b}.

The VFE ASICs are 16 SKIROC2 \cite{Callier:2011zz,Amjad:2014tha,Suehara:2018mqk}
(Silicon pin Kalorimeter Integrated ReadOut Chip), 
that have been designed for the readout of silicon PIN diodes.
The SKIROC2 in LFBGA package are bump bonded to the PCB.
The version of the ASUs tested in this beam test has a thickness
of 2.8 mm including the ASICs in its current packaging.
Each of these SKIROC2 comprises 64 readout channels
made of a variable-gain preamplifier followed by two branches:
a fast line for the self-trigger decision and a slow line for dual-gain charge measurement.
The gain on the preamplifier is set by changing the feedback capacitor, $C_{f}$.
The fast line consists of a high gain variable CRRC shaper followed by
a low offset discriminator to make the trigger decision.
A common 10-bit DAC provides the threshold of the discriminator.
The slow line is made of a low gain and a high gain CRRC
shapers to handle a large dynamic range.
When a channel triggers, a track and hold cell is used to record the signal at its peaking time
in the dual gain line. The levels of all the others
channels are then also recorded.
% A bandgap ensures the stability with
%respect to supply voltage and temperature for all the requested
%references in the analogue core.
The triggers are timestamped within each gated acquisition with a slow clock
of 5 MHz. The timestamp numbers are called bunch crossing identifiers (BCID).
The charges are stored in the buffers of a switched capacitor array, SCA, and later converted by a 12-bit Wilkinson ADC.
The ASIC consumes, in the power pulsing conditions as foreseen for the ILC, 
27 $\upmu$W per channel.

The four sensors consist of $90\times90$ mm$^{2}$ silicon sensors of
320$\pm15\,\upmu$m thick with high resistivity (larger than 5000 $\Omega\cdot$cm).
Each sensor is subdivided in an array of 256 PIN diodes of $5.5\times5.5$ mm$^2$
connected each to the PCB pads by a dot of conductive glue.
The high voltage to deplete the sensors is delivered to the sensors via a
100 $\upmu$m copper foil isolated from the rest of the setup by a kapton sheet.
It has been estimated that
a MIP traversing the PIN perpendicular to its surface produces, in average,
a signal of 4 fC.

@@

\begin{enumerate}
\item Calibration without tungsten absorber using 3 GeV positrons interacting, in the first approach, as MIPs.
  The beam was normally directed to 81 positions equally distributed over the modules surface.
\item Test in a magnetic field up 1 T using a 3 GeV positron beam.
  For this test, a PVC structure was designed and produced to support one single readout module
  without any tungsten plates.
\item Response to electrons of different energies with a fully equipped detector, {\it i.e}\@. sensitive parts {\it and} tungsten absorber. 
\end{enumerate}

In this paper, we discuss in detail the results of the commissioning of the prototype in Section \ref{sec:commissioning}
and the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
We also show the performance of the single readout tested in a magnetic field in Section \ref{sec:magnetic}. Finally,
a first look to the performance of the detector
in electromagnetic shower events is discussed in Section \ref{sec:showers}.

@@

\begin{figure}[h!]
  \includegraphics[width=0.5\textwidth]{masked_layer.eps} 
\caption{Fraction of channels with counts above one MIP in noise runs and that have been disabled for the data taking.}
\label{noisycells}
\end{figure}

@@

For each ASIC, the threshold of the internal trigger
was optimized by means of dedicated scans of trigger threshold values
with only noise signals or with injected signals of different amplitudes.
The scans start from high values of the thresholds
and this are lowered successively and the number of signals recorded
by each channel are counted. The resulting curves can be approximated by an inverted error function.
A value of the optimal threshold was calculated for every channel by shifting the threshold
from the threshold at the 50\% of the curve plus 3 times the width of the curve, 
with the width defined as half the difference between the thresholds
at which the curve is equal to $50\pm34\%$. The average of the optimal thresholds for all channels
is used as the optimal global threshold to be used by the ASIC.
If the analysis has failed in more than 50\% of the channels ({\it i.e.} because they are masked),
an {\it ad-hoc} high value of the threshold is chosen for the ASIC (250 in DAC units).

Note here that the width of the curve defined before depends on the ratio
of the frequency of the white noise of the electronics and the clock speed of the readout.
Therefore, this quantity is not the optimal estimator of the detector noise.
To achieve this the scan has to be repeated with external signals.
These can either be provided by signals generated by beam particles or by injecting signals into the channels.
Here we follow the second approach. Amplitudes equivalent to 1 and 2 MIPs were injected into channels of an ASIC mounted on a testboard.

The result of these scans is shown in Figure \ref{scurves_injection} for several channels of one SKIROCs.
These curves allow for the trigger threshold calibration and the
estimation of signal-over-noise ratio for the trigger, $(S/N)_{trigger}$, defined as the ratio between the distance of the
1 MIP and 2 MIP threshold curves scans at its 50\% of efficiency and the width of the 1 MIP threshold scan curve.
From the measurement shown in Figure \ref{scurves_injection} we extract a $(S/N)_{trigger}$ ratio of about 12.8.

\begin{figure}[h!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=0.5\textwidth]{scurve_pp_fastshaper_ch_DAC_labels.eps}\\ %{scurve_pp_fastshaper_ch_DAC-eps-converted-to.pdf} \\
	\end{tabular}
  \caption{Two sets of threshold curves. Each set consists of theshold curves for individual channels in which a charge is artifially injected using a pulse generator.
    For the set in the left (in blue), an equivalent of 1 MIP was injected. For the set in the right (red), a equivalent of 2 MIPs was injected.
    These curves were obtained in a dedicated testboard \cite{Suehara:2018mqk} to test single SKIROC2 ASICs.}
\label{scurves_injection}
\end{figure}

@@

\begin{figure}[h!t]
  \centering
  \includegraphics[width=0.5\textwidth]{threshold_chip.eps}
  \caption{Summary of the trigger threshold settings in the internal DAC units and in MIP units.}
\label{trigger_thresholds}
\end{figure}

@@

All the analyses presented here rely on the selection and identification
of tracks-like events. The first step of the reconstruction is the rejection
of two types of fake events due to the ASIC
design: {\it a)} triggers in consecutive BCIDs
due to the preamplifiers sensitivity to instabilities of the power supply; {\it b)}
an artefact of the event validation logical sequence of the ASIC. These fake
events are removed offline using timing information.
Residual electromagnetic showers are rejected by requiring
less than 5 triggers per module.
Tracks are therefore reconstructed by creating clustered
events from the seven layers grouped using their time stamp, allowing for a
tolerance on the BCID of $\pm1$. An event is accepted if at least
three of the layers were clustered together in a track traversing the modules in the
same position
for all modules with a tolerance of $\pm5.5$ {\rm mm} per layer.

@@

\begin{figure}[!t]
  \centering 
  \includegraphics[width=0.5\textwidth]{efficiency_nhits4_chips.eps} \\
  \caption{MIP detection efficiency in high purity samples of tracks of MIP-like acting particles for all layers. The average for all readout channels in each ASICs is shown. The error bars correspond to the standard deviation of the efficiency distribution of all channels in th ASIC.}
\label{efficiency}
\end{figure}

\subsection{Performance of a single readout module in a magnetic field}
\label{sec:magnetic}

The study of the performance of the module inside
inside magnetic fields has been divided in three consecutive steps:
a reference run without magnetic field; a run with a magnetic field of 1 T; a second run with 0.5 T; and a final run without, again, magnetic field.
The beam, 3 GeV positrons, was incident on the area of the PCB readout by the ASIC number 12.
During all this time, the readout module was continuously monitored and did not
show any technical issue or change of performance. Due to the lower beam rates in this area (and the technical character of the test)
we did not collect enough data to present a reliable comparison with the calibration described in the previous sections.
However, we got enough data to study in detail the stability of the pedestal position and width of all channels
in the ASIC 12. Their values are well compatible with the values obtained in Section \ref{sec:calib}.
This is shown in Figure \ref{pedestal_magnetic}.
We see that the agreement is perfect within the statistical uncertainties.
Due to the lower rates in this beam area, the
analysis is only done up to few memory cells.%and at least 500 entries are required in order to calculate the pedestals
%for comparison with the default values.

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=0.5\textwidth]{1T_summary_pedestal.eps} \\
    \includegraphics[width=0.5\textwidth]{1T_summary_noise.eps}
  \end{tabular}
  \caption{
    Average deviation of the pedestal mean position (up) and width (down) during the different runs at different magnetic field (1T, 0.5 T and 0T)
    compared with data taken outside of the magnet structure. The error bars correspond to one standard deviation of the averaged values.
    The results for several SCA is presented in each plot, with a slight shift in the $x$-axis to artificially separate the points for better visualization.
  }
\label{pedestal_magnetic}
\end{figure}

\subsection{Performance of the SiW-ECAL for low energy electromagnetic showers.}
\label{sec:showers}
For the last part of the beam test, the stack was equipped with several plates of tungsten of different thickness, interleaved
between the readout modules (including one also between the beam and the first module).
We performed several energy scans of the beam (1, 2, 3, 4, 5 and 5.8 GeV)
and directed it in different positions. In addition, also several distributions of the tungsten absorbers
were put in place. For the analysis of these data we proceed in a similar way than 
the described in Section \ref{sec:mip} for the event building by timestamp. In addition, the single cell calibration described in previous section is applied. In Section \ref{sec:mip}, the events with more than 5 triggers per module were rejected to remove shower like events from the sample, in the present analysis, no constrain on the number of triggers per layer was applied.
The results presented here correspond to the configuration of tungsten amounting 8.4 $X_{0}$ with the beam directed
to the area covered by ASICs number 12-15. For this run, we got enough data to
calculate with high statistics the shower profile for all the energies. This is presented in Figure \ref{showers}.
To calculate the shower profile, we used the the single cell calibration results presented in the previous sections.

\begin{figure}[!t]
  \centering
  \includegraphics[width=0.5\textwidth]{shower.eps}\\
  \caption{Electromagnetic shower profiles for different beam energies. In the x-axis, we show the accumulated thickness of tungsten absorber in front
    of evert active layer. In the y-axis, the averaged fraction of the total energy measured by every active layer in each electromagnetic shower event. }
\label{showers}
\end{figure}

@@

In this document we present the results
on the commissioning in beam of a small but fully equipped SiW-ECAL technological prototype
made of readout modules featuring the main characteristics foreseen for future high energy $e^{+}e^{-}$ collider detectors.
%It is the first time that results obtained with data taken by the SiW-ECAL continuosly
%operated in power pulsing are published.
%For the first time results
% SETUP dedicated for physics program with electromagnetic showers.
For the first time results are presented for detection units featuring 1024 channels as
designed for e.g. the ILD Detector in a setup optimized for a physics program dedicated to the study
of electromagnetic showers. The seven layers under study were operated in power pulsed mode.
Therefore this article constitutes a first reference for the detector performance in this operation mode.  
The beam test has allowed for studying in detail 
the performance of the detector.
The detector response is homogeneous with
98\% of the non masked channels calibrated
at a spread of the 5\%.
The signal over noise on the trigger has been evaluated to be about 12.8, a value that allows to
for setting trigger below the MIP level with high efficiency 
although new dedicated beam tests are required to know the uncertainty and spread
of this value 
among different modules and ASICS.
The signal over noise on the charge measurement for triggered channels is 20.4, which 
ensures that all channels with a trigger just about noise level can be used in the data analysis.
The MIP detection efficiency in tracks has been evaluated to be compatible with the 100\% in most of the channels.
This first approach to electromagnetic shower results looks promising although further studies and comparisons with simulations are foreseen
including the data of coming beam tests, which will include further R\&D developments and a potentially larger
stack with up to $\sim20-30$ fully equipped
layers and an homogeneous tungsten absorber distribution amounting up to $\sim24$ $X_{0}$ as foreseen, for example, by the ILD project
for the International Linear Collider.
